Price of Anarchy for Mean Field Games

### 2018-07-20 PoA.tex
proposition 5 finished!

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$. Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $. Then there exists $\bar{b}_2^* := \bar{b}_2^*(c_{b_2},t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < c_{b_2}$. Then $f(\bar{b}_2,t_2) - c_3 + 2c_{b_2} > c_{b_2}$ and 
	\begin{equation*}
	\begin{array}{rl}
		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
		& \leq  e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
	\end{array}
	\end{equation*}

 	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$. As before, and recycling notation, for any $\epsilon>0$, there exists a $\bar{b}_2^*:=\bar{b}_2^*(\epsilon,t_1) > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$. Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce:
 	$$ \vert u_{t_1}^{\bar{b}_2} \vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
 	$$

 	Idem, we can show that for $t_1 \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} =: c_4 >0,
	\end{split}
	\end{equation*}
	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$. Thus $ \vert w_{t_1}^{\bar{b}_2} \vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.

	Hence, together with the equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2 ,$$
	which implies that 
	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$

>>>>

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$. Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $. Then there exists $\bar{b}_2^* := \bar{b}_2^*(c_{b_2},t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < c_{b_2}$. Then $f(\bar{b}_2,t_2) - c_3 + 2c_{b_2} > c_{b_2}$ and 
	\begin{equation*}
	\begin{array}{rl}
		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
		& \leq  e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
	\end{array}
	\end{equation*}
	Let $\epsilon>0$. Then there exists a $\bar{b}_2^{**}>\bar{b}_2^{*}$, such that for all $\bar{b}_2>\bar{b}_2^{**}$, we have:
	\begin{equation}
	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }|<\epsilon.
	\label{eq:limit_p_f(p)}
	\end{equation}

 	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$. Given $\epsilon>0$, there exists a $\bar{b}_2^*:=\bar{b}_2^*(\epsilon,t_1) > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$. Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce:
 	$$ \vert u_{t_1}^{\bar{b}_2} \vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
 	$$

 	Idem, we can show that for $t_1 \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} =: c_4 >0,
	\end{split}
	\end{equation*}
	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$. Thus, $ \vert w_{t_1}^{\bar{b}_2} \vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.

	Hence, together with equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2.$$
	Thus, by taking $\epsilon \to 0$, we have:
	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$
